Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-08-03 paper/paper.Rmd
revised section 5.5 Summary

The non-spatial CV estimate of AUC (0.77) is around 0.15 better compared to the spatial CV estimate of 0.61.
The better performance score results from over-optimism in the estimation with NSpCV.
The actual predictive performance on new data is much more realistically reflected by the performance estimated via SpCV.
The magnitude of this difference is variable as it depends on the dataset, the magnitude of STAC and the learner itself.
Algorithms with a higher tendency of overfitting to the training set will have a larger spread in such scenarios.

The respective folds of the resamplings used in this example are shown in Figures&nbsp;\@ref(fig:vis-spcv) and&nbsp;\@ref(fig:vis-nspcv).

>>>>

The non-spatial CV estimate of AUC (0.77) is around 0.15 better compared to the spatial CV estimate of 0.61.
The better performance results from over-optimism in the estimation with non-spatial CV.
Spatial CV, in contrast, provides a better measure of a model's ability to generalize from the training sample --- in the Ecuador case study, from the hillslopes and historical landslides in the training sample.
It is also expected that spatial CV results better reflect the performance of a model on new, spatially separate data.
The magnitude of this difference may depend on the dataset, the strength on spatial or spatiotemporal autocorrelation, and the learner itself.
Algorithms with a higher tendency to overfit to the training set will tend to have a larger spread in such scenarios.

<!-- AB: TODO: Check if the following paragraphs overlaps with the Discussion section; perhaps merge into Discussion. -->
Since spatial CV can also be used for hyperparameter tuning in the \pkg{mlr3} framework, the model can be optimized to show an improved performance in a specific predictive setting [@schratz2019].
This may, for example, involve a reduced maximum tree depth in the Ecuador case study, since this leads to stronger generalization and reduced overfitting.
